### 2020-06-10 sections/frag/frag.tex
Noticed inaccuracies in the definition of resource projection + subsequent theorems.

Monotones reduce the structure of the resource theory $\R$ into a real number ordering.
Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
This is a generic approach that ensures a form of state comparison and resource quantification.
However, motivated by $\sigma$-fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
\begin{figure}[t]
    \centering
    \includegraphics[height=3cm]{sections/major/fragments.pdf}
    \caption{Fragments \nick{Split into subfigures}
    }
    \label{fig:fragments}
\end{figure}
We define such a resource projection for general resource theories as follows.
\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    Any subtheory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$ is called a resource fragment iff there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \cal{B}(\cal{H}) \mapsto \cal{B}(\cal{H})$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
    \end{enumerate}
    We call $\Pi$ a resource projection.
\end{definition}
Fragment $\R'$ is the image of the projection $\Pi$.
Considering a resource projection is particularly useful when the pre-order of the fragment is tractable.
Note the subtle difference of condition 1 in~\cref{def:fragment} and condition 2 in~\cref{def:mono}, which is due to fragments generally retaining a pre-order, while monotones impose a total order.

@@

	Let $\Pis = \M$.
	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}.

@@

We now justify the name $\sigma$-fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
\begin{proposition}
    Let $\R = (\F, \O)$ be a theory of magic.
    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
\end{proposition}
\begin{proof}
    Let the state projection be the identity projection $\Pis:\F\mapsto\F$.

    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

@@

Existing magic theories can be thought of as fragments of $\Rmax$.
\begin{proposition}
    Every theory of magic $\R$ is a fragment of the maximal theory $\Rmax$.
\end{proposition}
\begin{proof}
    Consider the state projection $\Pis:\Fmax \mapsto \F$, defined as
    \begin{equation}
    \Pis(\sigma) =
    \begin{cases}
        \sigma,\ &\sigma \in \F, \\
        \frac{1}{d}\id,\ &\sigma \notin \F.
    \end{cases}
    \end{equation}
    \nick{Perhaps $\Pis = $ identity}
    Let $1_{\rm{C}}$ denote the identity channel.
    Consider the operation projection $\Pio:\Omax \mapsto \O$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    The orderd pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

>>>>

Monotones reduce the structure of the resource theory $\R$ into a real number ordering.
Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
This is a generic approach that ensures a form of state comparison and resource quantification.
However, motivated by $\sigma$-fragments in magic theories, it is clear that we can often reduce the theory by a less \nick{information-collapsing} projection into a subtheory $\R'$ which has a tractable pre-order $\R'$, as sketched in~\cref{fig:fragments}.
\begin{figure}[t]
    \centering
    \includegraphics[height=3cm]{sections/major/fragments.pdf}
    \caption{Fragments \nick{Split into subfigures}
    }
    \label{fig:fragments}
\end{figure}
We define such a resource projection for general resource theories as follows.
\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    Any subtheory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$ is called a resource fragment iff there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \D \mapsto \D$ and $\Pis(\rho_2) \nprec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_{\R} \rho_2$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for all free operations $\E_1, \E_2 \in \O$.
    \end{enumerate}
    We call $\Pi$ a resource projection.
\end{definition}
Fragment $\R'$ is the image of the projection $\Pi$.
Considering a resource projection is particularly useful when the pre-order of the fragment is tractable.
Note the subtle difference of condition 1 in~\cref{def:fragment} and condition 2 in~\cref{def:mono}, which is due to fragments generally retaining a pre-order, while monotones impose a total order.

@@

	Let $\Pis = \M$.
	The defining properties of a monotone, given in~\cref{def:mono}, ensure condition 1 of~\cref{def:fragment}. \nick{expand}

@@

We now justify the name $\sigma$-fragment for the subdivision of a magic theory $\R = (\F, \O)$, by establishing a resource projection which reduces $\R$ into any subtheory $(\F, \O_\sigma)$.
\begin{proposition}
    Let $\R = (\F, \O)$ be a theory of magic.
    Every $\sigma$-fragment $(\F, \O_\sigma)$ is a resource fragment of $\R$.
\end{proposition}
\begin{proof}
    Let the state projection be the identity projection $\Pis:\D\mapsto\D$.

    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    \nick{$\Pio$ should be different, this here is not right. If we need to project every $\E \in \O$, we may need a different condition on $\Pio$ than $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$.}
    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

@@

Existing magic theories can be thought of as fragments of $\Rmax$.
\begin{proposition}
    Every theory of magic $\R$ is a fragment of the maximal theory $\Rmax$.
\end{proposition}
\begin{proof}
    \nick{We need a state projection that establishes that some free states are not free any more $+$ an operations projection.}
\end{proof}

### 2020-06-10 sections/magic/magic.tex
Noticed inaccuracies in the definition of resource projection + subsequent theorems.

We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
The structure of such theory is described by a pre-order, often called partial order \nick{CITE}, $\prec_{\R}$ between states.
We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.

>>>>

We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
Further denote by $\D$ the set of states considered under the theory, that is the union of free and resource states.
The structure of such theory is described by a partial order \nick{CITE}, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.
We further call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
The above notation will be used for general resource theories as well.

### 2020-06-10 sections/major/major.tex
Updated resource projection definition
Noticed inaccuracies in the definition of resource projection + subsequent theorems.

Let $\R = (\F, \O)$ be a general resource theory.
We call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. \nick{expand}

\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
    A subtheory $\R'$ of a magic theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} of $\R$ iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$. 
This is an observation arising from the stochastic nature of free operations. 
We now show that every free operation has a fixed point, so that the theory $\R$ can be entirely subdivided into $\sigma$-fragments.

@@

\begin{theorem}
    Let $\R = (\O, \F)$ be a theory of magic.
    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible. 
    Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
\end{theorem}
\begin{proof}
    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
\end{proof}

@@

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{sections/major/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so neither $\bmx \prec_{\bmd} \bmy$ nor $\bmy \prec_{\bmd} \bmx$.
    \nick{Recast in terms of magic}
    }
    \label{fig:lctoy}
\end{figure}

@@

\emph{Remark 2.} Similarly, not all stochastic matrices correspond to $\cpos$ operations.

As an example, consider the permutation matrix
\begin{equation}
    \Pi_X = \begin{psmallmatrix}
        0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0
    \end{psmallmatrix} \otimes \begin{psmallmatrix}
        0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0    
    \end{psmallmatrix} \in \stochw,\ d=5.
\end{equation}
It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any completely positive operation and therefore to any $\E \in \O$, due to~\cref{thm:frag}.

>>>>

Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
This observation gives rise to the idea of subdividing magic theories into ``chunks'' identified by the invariance of a particular state under stochastic processes. \nick{explain better}
\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
    A subtheory $\R'$ of a magic theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} of $\R$ iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that leave $\sigma$ invariant,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

State $\sigma$ is thus a fixed point of all operations in $\O_\sigma$. 
We now show that every free operation has a fixed point, so that the theory $\R$ can be entirely subdivided into $\sigma$-fragments.

@@

\begin{theorem}
    Let $\R = (\F, \O)$ be a theory of magic.
    Suppose the state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible, $\tau \prec_\R \rho$.
    Then, there exists a full-rank free state $\sigma \in \F$ such that  $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
\end{theorem}
\begin{proof}
    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
\end{proof}

@@

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{sections/major/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic}
    }
    \label{fig:lctoy}
\end{figure}

@@

\emph{Remark 2.} Similarly, not all stochastic matrices correspond to completely positive operations.

As an example, consider the permutation matrix
\begin{equation}
    \Pi_X = \begin{psmallmatrix}
        0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & 0 & 0
    \end{psmallmatrix} \otimes \begin{psmallmatrix}
        0 & 0 & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & 1 \\
        0 & 0 & 0 & 1 & 0 \\
        1 & 0 & 0 & 0 & 0 \\
        0 & 1 & 0 & 0 & 0    
    \end{psmallmatrix} \in \stochw,\ d=5.
\end{equation}
It preserves the uniform distribution $\W{\frac{1}{5}\id}{}$, but it does not correspond to any $\cpos$ operation, hence any $\E \in \O$ due to~\cref{thm:frag}.
